### 2012-03-01 Krantz-v3/Chapters/chapter1/experiments.tex
INITIAL SUBMISSION VERSION

The specific dataset we report results for in this chapter was gathered from the NewYork-Presbyterian Hospital clinical data warehouse. 
It consists of 6,000 discharge summaries and
their associated ICD-9 codes (7,298 distinct codes overall), representing all
the discharges from the hospital in 2009. All included discharge summaries had associated ICD-9 Codes.
Summaries have 8.39 associated ICD-9
codes on average (std dev=5.01) and contain an average of 536.57 terms after
preprocessing (std dev=300.29). We split our dataset into 5,000 discharge
summaries for training and 1,000 for testing.

@@

Amazon.com is one such retailer.  Their product categorization data is available as part of the 
 Stanford Network Analysis Platform (SNAP) dataset~\cite{SNAP}.    A representative sub-tree of the amazon.com DVD produce categorization tree is shown in Figure \ref{fig:product_tree}.  
Product descriptions were obtained separately from the
Amazon.com website directly. Once such description is
\begin{quote}
{Winner of five Academy Awards, including Best Picture and Best Director, The Deer Hunter 
is simultaneously an audacious directorial conceit and one of the greatest films ever made 
about friendship and the personal impact of war. Like Apocalypse Now, it's hardly a conventional 
battle film--the soldier's experience was handled with greater authenticity in Platoon--but its 
depiction of war on an intimate scale packs a devastatingly dramatic punch ... }
\end{quote}
We study the collection of DVDs
in the product catalog specifically.
%We were able to deduce the structure of the
%hierarchy for the Amazon.com products because all ancestors in the
%hierarchy were included with each category label. For example, {}``DVD / Genres
%/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
%for the DVD, {}``The Time Machine.''
The resulting dataset contains 15,130 product descriptions for training and 1,000
for testing. The product descriptions consist of
91.89 terms on average (std dev=53.08). Overall, there are 2,691 unique categories.
Products are assigned on average 9.01 categories (std dev=4.91). The vocabulary
consists of the most frequent 30,000 words omitting stopwords.

@@

In each case the gold standard for testing was derived from the test data. To make the comparison as antagonistic to HSLDA as possible (relative to the other models), ancestors of
observed nodes in the label hierarchy were ignored, observed nodes were
considered positive and descendants of observed nodes were assumed to be
negative. Note that this is different from our treatment of the observations during inference where we marginalize over possible settings of unobserved labels.
For instance, as the SLDA model does not enforce hierarchical
label constraints, when we consider only observed nodes we penalize HSLDA.  This is because
 the is-a hierarchical constraints say that the ancestors of positively labeled nodes must also be positive which the SLDA model cannot guarantee.
Another antagonism of this gold standard is that it is likely to inflate the number of false positives because
the labels applied to any particular document are usually not as complete as
they could be.  ICD-9 codes, for instance, are known to lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as
false positives~\cite{Birmetal2005}.
However, given that the label space is often large (as in our examples) it is a
reasonable assumption that erroneous false positives should not skew results
significantly.

@@

Figure~\ref{fig:1a} demonstrates the performance of the model on the clinical data as an ROC curve varying $\mu$.  For instance, 
a hyperparameter setting of $\mu=-1.6$ yields the following performance:
the full HSLDA model had a 
true positive rate of 0.57 and a false positive rate of 0.13, the SLDA model
had a true positive rate of 0.42 and a false positive rate of 0.07, and the
HSLDA model where LDA and the regressions were fit separately had a true
positive rate of 0.39 and a false positive rate of 0.08. These points are highlighted in Figure~\ref{fig:1a}.

@@

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline
MASS & WOUND \\
\hline
CANCER & FOOT \\
\hline
RIGHT & CELLULITIS \\
\hline
BREAST & ULCER \\
\hline
CHEMOTHERAPY & LEFT \\
\hline
METASTATIC & ERYTHEMA \\
\hline
LEFT & PAIN \\
\hline
LYMPH & SWELLING \\
\hline
TUMOR & SKIN \\
\hline
BIOPSY & RIGHT \\
\hline
CARCINOMA & ABSCESS \\
\hline
LUNG & LEG \\
\hline
CHEMO & OSTEOMYELITIS \\
\hline
ADENOCARCINOMA & TOE \\
\hline
NODE & DRAINAGE \\
\hline
\end{tabular}
\end{extract}

@@

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline
SERIES & BASEBALL \\
\hline
EPISODES & TEAM \\
\hline
SHOW & GAME \\
\hline
SEASON & PLAYERS \\
\hline
EPISODE & BASKETBALL \\
\hline
FIRST & SPORT \\
\hline
TELEVISION & SPORTS \\
\hline
SET & NEW \\
\hline
TIME & PLAYER \\
\hline
TWO & SEASON \\
\hline
SECOND & LEAGUE \\
\hline
ONE & FOOTBALL \\
\hline
CHARACTERS & STARS \\
\hline
DISC & FANS \\
\hline
GUEST & FIELD \\
\hline
\end{tabular}
\end{extract}

>>>>

The specific dataset we report results for in this chapter was gathered from the NewYork-Presbyterian Hospital clinical data warehouse. 
It consists of 6,000 discharge summaries and
their associated ICD-9 codes (7,298 distinct codes overall), representing a portion of
the discharges from the hospital in 2009. All included discharge summaries had associated ICD-9 Codes.
Summaries have 8.39 associated ICD-9
codes on average (std dev=5.01) and contain an average of 536.57 terms after
preprocessing (std dev=300.29). We split our dataset into 5,000 discharge
summaries for training and 1,000 for testing.

@@

Amazon.com is one such retailer.  Their product categorization data is available as part of the 
 Stanford Network Analysis Platform (SNAP) dataset~\cite{SNAP}.    A representative sub-tree of the amazon.com DVD product category tree is shown in Figure \ref{fig:product_tree}.  
Product descriptions were obtained separately from the
Amazon.com website directly. Once such description is
\begin{quote}
{Winner of five Academy Awards, including Best Picture and Best Director, The Deer Hunter 
is simultaneously an audacious directorial conceit and one of the greatest films ever made 
about friendship and the personal impact of war. Like Apocalypse Now, it's hardly a conventional 
battle film--the soldier's experience was handled with greater authenticity in Platoon--but its 
depiction of war on an intimate scale packs a devastatingly dramatic punch ... }
\end{quote}
We study the collection of DVDs
in the product catalog specifically.
%We were able to deduce the structure of the
%hierarchy for the Amazon.com products because all ancestors in the
%hierarchy were included with each category label. For example, {}``DVD / Genres
%/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
%for the DVD, {}``The Time Machine.''
The resulting dataset contains 15,130 product descriptions for training and 1,000
for testing. The product descriptions consist of
91.89 terms on average (std dev=53.08). Overall, there are 2,691 unique categories.
Products are assigned on average 9.01 categories (std dev=4.91). The vocabulary
consists of the most frequent 30,000 words omitting stopwords.

@@

In each case the gold standard for testing was derived from the test data. To make the comparison as antagonistic to HSLDA as possible (relative to the other models), in evaluation only, ancestors of
observed nodes in the label hierarchy were ignored, observed nodes were
considered positive and descendants of observed nodes were assumed to be
negative. Note that this is different from our treatment of the observations during inference where we marginalize over possible settings of unobserved labels.
For instance, as the SLDA model does not enforce hierarchical
label constraints, when we consider only observed nodes we penalize HSLDA.  This is because
 the is-a hierarchical constraints say that the ancestors of positively labeled nodes must also be positive which the SLDA model cannot guarantee.
Another antagonism of this gold standard is that it is likely to inflate the number of false positives because
the labels applied to any particular document are usually not as complete as
they could be.  ICD-9 codes, for instance, are known to lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as
false positives~\cite{Birmetal2005}.
However, given that the label space is often large (as in our examples) it is a
reasonable assumption that erroneous false positives should not skew results
significantly.

@@

Figure~\ref{fig:1a} demonstrates the performance of the model on the clinical data as an ROC curve varying $\mu$.  For instance, 
a hyperparameter setting of $\mu=-1.6$ yields the following performance:
the full HSLDA model had a 
true positive rate of 0.57 and a false positive rate of 0.13, the SLDA model
had a true positive rate of 0.42 and a false positive rate of 0.07, and the
HSLDA model where LDA and the regressions were fit separately had a true
positive rate of 0.39 and a false positive rate of 0.08. These points are highlighted in Figure~\ref{fig:1a}.  Note that the figure is somewhat misleading because for any one value of $\mu$ HSLDA outperforms the comparison models by a relatively large margin.

@@

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline \hline
MASS & WOUND \\
\hline
CANCER & FOOT \\
\hline
RIGHT & CELLULITIS \\
\hline
BREAST & ULCER \\
\hline
CHEMOTHERAPY & LEFT \\
\hline
METASTATIC & ERYTHEMA \\
\hline
LEFT & PAIN \\
\hline
LYMPH & SWELLING \\
\hline
TUMOR & SKIN \\
\hline
BIOPSY & RIGHT \\
\hline
CARCINOMA & ABSCESS \\
\hline
LUNG & LEG \\
\hline
CHEMO & OSTEOMYELITIS \\
\hline
ADENOCARCINOMA & TOE \\
\hline
NODE & DRAINAGE \\
\hline
\end{tabular}
\end{extract}

These topics closely correspond to common clinical concepts, namely, cancers of the thorax and wounds common to diabetics suffering from poor peripheral circulation.  Evaluations of the subject coherence of these topics relative to baselines are ongoing, but early results suggest positive findings similar to those reported for other supervised LDA models.

@@

\begin{extract}
\begin{tabular}{|c|c|}
\hline
\textbf{Topic 1} & \textbf{Topic 2} \\ \hline \hline
SERIES & BASEBALL \\
\hline
EPISODES & TEAM \\
\hline
SHOW & GAME \\
\hline
SEASON & PLAYERS \\
\hline
EPISODE & BASKETBALL \\
\hline
FIRST & SPORT \\
\hline
TELEVISION & SPORTS \\
\hline
SET & NEW \\
\hline
TIME & PLAYER \\
\hline
TWO & SEASON \\
\hline
SECOND & LEAGUE \\
\hline
ONE & FOOTBALL \\
\hline
CHARACTERS & STARS \\
\hline
DISC & FANS \\
\hline
GUEST & FIELD \\
\hline
\end{tabular}
\end{extract}

### 2012-03-01 Krantz-v3/Chapters/chapter1/inference.tex
touched all kinds of good stuff... ready for adler's final contributions.
fixed a few typos
INITIAL SUBMISSION VERSION

\label{sec:inference}
Our inference goal  is to obtain a representation of the posterior distribution
of the latent variables in the model.  The posterior distribution we seek does not have a simple analytic form from which exact samples can be drawn.
This is usually the case for posterior distributions of non-trivial
probabilistic models and suggests a approximating the posterior distribution by sampling.

In this section we derive the conditional distributions required to sample from the HSLDA posterior distribution using Markov chain Monte Carlo.  A very brief review of Markov chain Monte Carlo can be found in Section \ref{sec:mcmc} at the end of this chapter.

The HSLDA sampler, like the collapsed Gibbs samplers for LDA \cite{Griffiths04}, is itself a collapsed Gibbs sampler in which all of the latent variables that can be analytically marginalized are.  Among others, the parameters $\boldsymbol{\phi}_{1:K}$
and $\boldsymbol{\theta}_{1:D}$ are analytically marginalized prior to deriving the following conditional distributions for sampling.  
  It will often be the
case that the set of labels $\mathcal{L}$ is not fully observed for
every document. We will define $\mathcal{L}_{d}$ to be the subset
of labels which have been observed for document $d$. In an is-a hierarchical regression  it is straightforward
to marginalize the variables $a_{l^{\prime},d}$ and $y_{l^{\prime},d}$
for $l^{\prime}\in\mathcal{L}\backslash\mathcal{L}_{d}$ simply by ignoring them. 
%We can also integrate out the parameters $\boldsymbol{\phi}_{1:K}$
%and $\boldsymbol{\theta}_{1:D}$ as in \cite{Griffiths04}.
 The remaining latent variables (those that are not collapsed out) are $\mathbf{z}=\{z_{1:N_{d},d}\}_{d=1,\ldots,D},\boldsymbol\eta=\{\boldsymbol\eta_{l}\}_{l\in\mathcal{L}},\mathbf{a}=\{a_{l^{\prime},d}\}_{l^{\prime}\in\mathcal{L}_{d},d=1,\ldots,D},\boldsymbol\beta,\alpha,\alpha^{\prime}$
and $\gamma$.

@@

\subsection{Gibbs Sampler}
 Let $\mathbf{a}$ be the set of all auxiliary variables, $\mathbf{w}$  the set of all words, $\boldsymbol\eta$  the set of all regression coefficients, and  $\mathbf{z}\backslash z_{n,d}$  the set $\mathbf{z}$ with element $z_{n,d}$ removed.  %The conditional posterior distribution of the latent topic indicators is
 We use the notation $\mathbf{z}_{-(n,d)}$ to
denote $\mathbf{z}_d\backslash z_{n,d}$. %, marginalizing
%$\theta_{1:D}$ and $\phi_{1:K}$. For details regarding collapsing
%in LDA models see \cite{Griffiths04}.

@@

First we consider the conditional distribution of $z_{n,d}$ (the assignment variable
for each word $n=1,\ldots,N_{d}$ in documents $d=1,\ldots,D$). 
%The
%conditional distribution does not include $\theta_{1:D}$ and $\phi_{1:K}$
%because they have been integrated out as in the collapsed Gibbs sampler
%\cite{Griffiths04}. 
%The conditional distribution of $z_{n,d}$ is
%proportional to the joint distribution of its markov blanket. \begin{equation}
%p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\propto p\left(z_{d,n},\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\end{equation}
Following the factorization of the model (refer again to Figure~\ref{fig:graphical_model}), we can write
\begin{eqnarray*}
\lefteqn{p\left(z_{n,d}\mid\mathbf{z}_d\backslash z_{n,d},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)}\\
&\propto&\prod_{l\in\mathcal{L}_{d}}p\left(a_{l,d}\mid\mathbf{z},\boldsymbol\eta_{l}\right)p\left(z_{n,d}\ |\ \mathbf{z}_d\backslash z_{n,d},\mathbf{a},\mathbf{w},\alpha,\boldsymbol\beta,\gamma\right).\end{eqnarray*}
 The product is only over the subset of labels $\mathcal{L}_{d}$
which have been observed for document $d$. By isolating terms that
depend on $z_{n,d}$ and absorbing all other terms into a normalizing
constant as in \cite{Griffiths04} we find 
\begin{eqnarray}
\lefteqn{p\left(z_{n,d}=k\mid\mathbf{z}\backslash z_{n,d},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\propto} \label{eq:z-likelihood} \\
 & \hspace{2cm}\left(c_{\left(\cdot\right),d}^{k,-\left(n,d\right)}+\alpha\boldsymbol\beta_{k}\right)\frac{c_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}+\gamma}{\left(c_{\left(\cdot\right),\left(\cdot\right)}^{k,-\left(n,d\right)}+V\gamma\right)}\prod_{l\in\mathcal{L}_{d}}\exp\left\{ -\frac{\left(\bar{\mathbf{z}}_{d}^{T}\boldsymbol\eta_{l}-a_{l,d}\right)^{2}}{2}\right\}\nonumber\end{eqnarray}
 where $c_{v,d}^{k,-\left(n,d\right)}$ is the number
of words of type $v$ in document $d$ assigned to topic $k$ omitting
the $n$th word of document $d$. The subscript $(\cdot)$'s
indicate to sum over the range of the replaced variable, i.e.~$ {c_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}} = \sum_d {c_{w_{n,d},d}^{k,-\left(n,d\right)}}$.  Here $\mathcal{L}_{d}$ is the set of labels which are observed for document $d$.  We sample from \eqref{eq:z-likelihood}  by enumeration and implicit normalization.
%
%Given Equation \ref{eq:z-likelihood}, $p\left(z_{d,n}\mid\mathbf{z}_{-\left(d,n\right)},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)$
%can be sampled through enumeration.

>>>>

\label{sec:inference}
Our inference goal  is to obtain a representation of the posterior distribution
of the latent variables in the model.  The posterior distribution we seek does not have a simple analytic form from which exact samples can be drawn.
This is usually the case for posterior distributions of non-trivial
probabilistic models and suggests approximating the posterior distribution by sampling.

In this section we derive the conditional distributions required to sample from the HSLDA posterior distribution using Markov chain Monte Carlo.  %A very brief review of Markov chain Monte Carlo can be found in Section \ref{sec:mcmc} at the end of this chapter.  
%
The HSLDA sampler, like the collapsed Gibbs samplers for LDA \cite{Griffiths04}, is itself a collapsed Gibbs sampler in which all of the latent variables that can be analytically marginalized are.  Among others, the parameters $\boldsymbol{\phi}_{1:K}$
and $\boldsymbol{\theta}_{1:D}$ are analytically marginalized prior to deriving the following conditional distributions for sampling.  
  It will often be the
case that the set of labels $\mathcal{L}$ is not fully observed for
every document. We will define $\mathcal{L}_{d}$ to be the subset
of labels which have been observed for document $d$. In an is-a hierarchical regression  it is straightforward
to marginalize the variables $a_{l^{\prime},d}$ and $y_{l^{\prime},d}$
for $l^{\prime}\in\mathcal{L}\backslash\mathcal{L}_{d}$ simply by ignoring them. 
%We can also integrate out the parameters $\boldsymbol{\phi}_{1:K}$
%and $\boldsymbol{\theta}_{1:D}$ as in \cite{Griffiths04}.
 The remaining latent variables (those that are not collapsed out) are $\mathbf{z}=\{z_{1:N_{d},d}\}_{d=1,\ldots,D},\boldsymbol\eta=\{\boldsymbol\eta_{l}\}_{l\in\mathcal{L}},\mathbf{a}=\{a_{l^{\prime},d}\}_{l^{\prime}\in\mathcal{L}_{d},d=1,\ldots,D},\boldsymbol\beta,\alpha,\alpha^{\prime}$
and $\gamma$.

@@

\subsection{Gibbs Sampler}
 Let $\mathbf{a}$ be the set of all auxiliary variables, $\mathbf{w}$  the set of all words, $\boldsymbol\eta$  the set of all regression coefficients, and  $\mathbf{z}\backslash z_{n,d}$  the set $\mathbf{z}$ with element $z_{n,d}$ removed.  %The conditional posterior distribution of the latent topic indicators is
 %We use the notation $\mathbf{z}_{-(n,d)}$ to
%denote $\mathbf{z}_d\backslash z_{n,d}$. %, marginalizing
%$\theta_{1:D}$ and $\phi_{1:K}$. For details regarding collapsing
%in LDA models see \cite{Griffiths04}.

@@

First we consider the conditional distribution of $z_{n,d}$ (the assignment variable
for each word $n=1,\ldots,N_{d}$ in documents $d=1,\ldots,D$). 
%The
%conditional distribution does not include $\theta_{1:D}$ and $\phi_{1:K}$
%because they have been integrated out as in the collapsed Gibbs sampler
%\cite{Griffiths04}. 
%The conditional distribution of $z_{n,d}$ is
%proportional to the joint distribution of its markov blanket. \begin{equation}
%p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\propto p\left(z_{d,n},\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\end{equation}
Following the factorization of the model (refer again to Figure~\ref{fig:graphical_model}), we can write
\begin{eqnarray*}
\lefteqn{p\left(z_{n,d}\mid\mathbf{z}_d\backslash z_{n,d},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)}\\
&\propto&\prod_{l\in\mathcal{L}_{d}}p\left(a_{l,d}\mid\mathbf{z},\boldsymbol\eta_{l}\right)p\left(z_{n,d}\ |\ \mathbf{z}_d\backslash z_{n,d},\mathbf{a},\mathbf{w},\alpha,\boldsymbol\beta,\gamma\right).\end{eqnarray*}
 The product is only over the subset of labels $\mathcal{L}_{d}$
which have been observed for document $d$. By isolating terms that
depend on $z_{n,d}$ and absorbing all other terms into a normalizing
constant as in \cite{Griffiths04} we find 
\begin{eqnarray}
\lefteqn{p\left(z_{n,d}=k\mid\mathbf{z}\backslash z_{n,d},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)\propto} \label{eq:z-likelihood} \\
 & \hspace{2cm}\left(c_{\left(\cdot\right),d}^{k,-\left(n,d\right)}+\alpha\boldsymbol\beta_{k}\right)\frac{c_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}+\gamma}{\left(c_{\left(\cdot\right),\left(\cdot\right)}^{k,-\left(n,d\right)}+V\gamma\right)}\prod_{l\in\mathcal{L}_{d}}\exp\left\{ -\frac{\left(\bar{\mathbf{z}}_{d}^{T}\boldsymbol\eta_{l}-a_{l,d}\right)^{2}}{2}\right\}\nonumber\end{eqnarray}
 where $c_{v,d}^{k,-\left(n,d\right)}$ is the number
of words of type $v$ in document $d$ assigned to topic $k$ omitting
the $n$th word of document $d$. The subscript $(\cdot)$'s
indicate to sum over the range of the replaced variable, i.e.~$ {c_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}} = \sum_d {c_{w_{n,d},d}^{k,-\left(n,d\right)}}$.  Here $\mathcal{L}_{d}$ is the set of labels which are observed for document $d$.  We sample from \eqref{eq:z-likelihood}  by first enumerating $z_{n,d}$ and then normalizing.
%
%Given Equation \ref{eq:z-likelihood}, $p\left(z_{d,n}\mid\mathbf{z}_{-\left(d,n\right)},\mathbf{a},\mathbf{w},\mathbf{\boldsymbol\eta},\alpha,\boldsymbol\beta,\gamma\right)$
%can be sampled through enumeration.

### 2012-03-01 Krantz-v3/Chapters/chapter1/probit.tex
INITIAL SUBMISSION VERSION

The range of the normal cdf is $(0,1)$ which means that it can be interpreted as a probability.  For instance, one can construct a generalized linear classification model (a ``probit regression model'') of the form 
\begin{equation}
P(y_i = 1) = \Phi(x_i^T\beta; 0, \sigma^2). \label{eqn:probit}
\end{equation}  Depending on convention (i.e. binary $y_i$ represented as $\{1,0\}$ or $\{1,-1\}$) then the probability of $y_i$ being labeled the opposite way is $P(y_i = -1)$ or $P(y_i = 0) = 1 - P(y_i=1).$  Here $x_i$ is a vector of covariates, $\beta$ is a vector of weights, and $y_i$ is a single, binary valued response.  As always, the close relationship between regression and classification are in full display here : probit regression is a ``generalized linear {\em regression} model'' as well as a ``binary classifier.''

%Figure \ref{fig:probit_no_aux_vars} shows the graphical model for probit regression (minus any priors on the regression weights $\beta$).   
 In this model we would like to use labeled training data, $\{x_i, y_i\}_{i=1}^N$ to ``learn'' the value of $\beta$ and then to use this value to predict the value of $y_{N+1} | x_{N+1}, \beta.$  If we are being Bayesian about our inference here what we really mean is that we will average over the posterior distribution of $\beta$ when making predictions.  This means that we want to draw samples from the posterior distribution of $\beta | \{x_i, y_i\}_{i=1}^N$.  To to this efficiently one can introduce a set of auxiliary variables $\{u_i\}_{i=1}^N$.  
 %In this note we will demonstrate that the model in  Figure \ref{fig:probit} is the same as the model in Figure \ref{fig:probit_no_aux_vars}  when the $u_i$'s are marginalized out and will suggest that inference in the former is computationally easier.

>>>>

The range of the normal cdf is $(0,1)$ which means that it can be interpreted as a probability.  For instance, one can construct a generalized linear classification model (a ``probit regression model'') of the form 
\begin{equation}
P(y_i = 1) = \Phi(x_i^T\beta; 0, \sigma^2). \label{eqn:probit}
\end{equation}  Depending on convention (i.e. binary $y_i$ represented as $\{1,0\}$ or $\{1,-1\}$) then the probability of $y_i$ being labeled the opposite way is $P(y_i = -1)$ or $P(y_i = 0) = 1 - P(y_i=1).$  Here $x_i$ is a vector of covariates, $\beta$ is a vector of weights, and $y_i$ is a single, binary valued response.  The close relationship between regression and classification are in full display here : probit regression is a ``generalized linear {\em regression} model'' as well as a ``binary classifier.''

%Figure \ref{fig:probit_no_aux_vars} shows the graphical model for probit regression (minus any priors on the regression weights $\beta$).   
 In this model we would like to use labeled training data, $\{x_i, y_i\}_{i=1}^N$ to ``learn'' the value of $\beta$ and then to use this value to predict the value of $y_{N+1} | x_{N+1}, \beta.$  Being Bayesian about inference means that we will average over the posterior distribution of $\beta$ when making predictions.  This means that we want to draw samples from the posterior distribution of $\beta | \{x_i, y_i\}_{i=1}^N$.  To to this efficiently one can introduce a set of auxiliary variables $\{u_i\}_{i=1}^N$.  
 %In this note we will demonstrate that the model in  Figure \ref{fig:probit} is the same as the model in Figure \ref{fig:probit_no_aux_vars}  when the $u_i$'s are marginalized out and will suggest that inference in the former is computationally easier.

### 2012-03-01 Krantz-v3/Chapters/chapter1/related_work.tex
INITIAL SUBMISSION VERSION

This chapter covers classifying or, equivalently, labeling bag-of-words data.  We show how to construct classifiers based on features derived from mixed membership models.  We specifically develop a solution to the concrete problem of hierarchically classifying text documents.  The model and techniques developed in this chapter can be used to solve any labeling or hierarchical classification problem involving data represented as bags-of-words.  For instance,  if an image is represented by counts of features then it can be described as being in a bag-of-words representation.   So, hierarchical classification of images might be tackled using the techniques developed in this chapter, although, such a particular application will not be explicitly considered.

We should agree that classification and regression are largely the same.  Namely, classification is regression with discrete output.  To solve classification problems we must learn from training instances, as in regression, a function $f : \mathcal{X} \rightarrow \mathcal{L}$ which maps from an input space $\mathcal{X}$ to an output (label) space $\mathcal{L}$.   For example, consider the problem of identifying the authors of a set of documents for which the true author is unknown but is one of a set of possible authors.   For such a problem the input space is the richly structured space of possible texts and the output space is the large but largely unstructured list of possible authors.  Training data would consist of text author pairs for texts known to have been authored by authors in the list of possible authors.

>>>>

This chapter covers classifying and labeling bag-of-words data.  %We show how to construct classifiers based on features derived from mixed membership models.  
We specifically develop a solution to the concrete problem of hierarchically classifying text documents.  The model and techniques developed in this chapter can be used to solve any labeling or hierarchical classification problem involving data represented as bags-of-words.  For instance,  if an image is represented by counts of features then it can be described as being in a bag-of-words representation.   So, hierarchical classification of images might be tackled using the techniques developed in this chapter, although, such a particular application will not be explicitly considered.

%We should agree that classification and regression are largely the same.  Namely, classification is regression with discrete output.  
To solve classification problems we must learn from training instances, as in regression, a function $f : \mathcal{X} \rightarrow \mathcal{L}$ which maps from an input space $\mathcal{X}$ to an output (label) space $\mathcal{L}$.   For example, consider the problem of identifying the authors of a set of documents for which the true author is unknown but is one of a set of possible authors.   For such a problem the input space is the richly structured space of possible texts and the output space is the large but largely unstructured list of possible authors.  Training data would consist of text/author pairs for texts known to have been authored by authors in the list of possible authors.
